---
title: "Chapter2-analyses"
format: 
  html:
    toc: true
execute: 
  echo: false
editor: visual
---

```{r}
#| echo: false
#| output: false
source("otter_data.R")
library(ggplot2) 
library(GGally) 
library(car)
library(dplyr)
library(DHARMa)
library(ggeffects)

df_latT |>
  group_by(site.location, latrine.present) |>
  summarise(count = n())

df_latPlot |>
  group_by(site.location, latrine.present) |>
  summarise(count = n())

```

# Data

```{r}
str(df_latT)
```

# Exploratory Data Analysis

## Outliers - box/violin plots

::: panel-tabset
### All

```{r}
ggplot(df_latPlot, aes(name, value, fill = name)) + geom_boxplot() + facet_grid(site.location ~ latrine.present)
```

### Forage Area

```{r}
ggplot(df_latT, aes(site.location, dforagearea)) + 
  geom_violin() + 
  facet_grid(~latrine.present)
```

### Freshwater

```{r}
ggplot(df_latT, aes(site.location, dfreshwater)) + 
  geom_violin() + 
  facet_grid(~latrine.present)
```

### Logging

```{r}
ggplot(df_latT, aes(site.location, dlogging)) + 
geom_violin() + 
  facet_grid(~latrine.present)
```

### Road

```{r}
ggplot(df_latT, aes(site.location, droad)) + 
  geom_violin() + 
  facet_grid(~latrine.present)
```

### Streammouth

```{r}
ggplot(df_latT, aes(site.location, dstreammouth)) + 
  geom_violin() + 
  facet_grid(~latrine.present)
```
:::

## Outliers-Cleavland

::: panel-tabset
### Road

```{r}
ggplot(df_latT, aes(droad, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```

### Cabin

```{r}
ggplot(df_latT, aes(dcabin, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```

### Logging

```{r}
ggplot(df_latT, aes(dlogging, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```

### Stream

```{r}
ggplot(df_latT, aes(dstreammouth, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```

### Freshwater

```{r}
ggplot(df_latT, aes(dfreshwater, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```

### Forage Area

```{r}
ggplot(df_latT, aes(dforagearea, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```
:::

::: panel-tabset
### zeros

```{r}
table(df_latT$lat.pres, df_latT$site.location) 
```

### collinearity/relationship

```{r}
Scatter_Matrix <- ggpairs(df_latT,columns = c(2:7, 9), title = "Scatter Plot Matrix for latrine Dataset", axisLabels = "show") 
Scatter_Matrix
```
:::

## Interactions

Not sure what to do with this yet

# Analysis

```{r}
m1 <- glm(lat.pres ~ droad + site.location + dlogging, 
          family = binomial(link = "logit"),
          data = df_latT)
```

## Diagnostics

::: panel-tabset
## Homogeneity-normality

```{r}
m1_simres <- simulateResiduals(m1) # str(bt_den.glmm1_simres,1) 
plot(m1_simres) 
```

## Independence
:::

## 

## Confirmatory Statistics

::: panel.tabset
## Summary

```{r} summary(m1)}
```

## Coefficients

```{r} coef(m1)}
```
:::

## Predictions

::: panel-tabset
### Road

```{r}
ggpredict(m1, terms = "droad") |> plot()
```

### Logging

```{r}
ggpredict(m1, terms = "dlogging") |> plot()
```

### Site

```{r}
ggpredict(m1, terms = "site.location") |> plot()
```

### Interaction

```{r}
ggpredict(m1, terms = c("site.location", "droad")) |> plot()
```
:::

## 
