---
title: "Chapter2-analyses"
format: 
  html:
    toc: true
    code-line-numbers: true
execute: 
  echo: false
editor: visual
---

```{r}
#| echo: false
#| output: false
source("otter_data.R")
library(ggplot2) 
library(GGally) 
library(car)
library(dplyr)
library(DHARMa)
library(ggeffects)

df_latT |>
  group_by(site.location, latrine.present) |>
  summarise(count = n())

df_latPlot |>
  group_by(site.location, latrine.present) |>
  summarise(count = n())

```

# Data

::: panel.tabset
## Structure

```{r}
str(df_latT)
```

## Contingency table

```{r}
df_latT |>
  group_by(site.location, latrine.present) |>
  summarise(count = n())

df_latPlot |>
  group_by(site.location, latrine.present) |>
  summarise(count = n())
```

## Tree Height

```{r}
table(df_latT$site.location, df_latT$latrine.present, df_latT$treeheight)
ggplot(df_latT, aes(x = treeheight)) + geom_bar() + facet_grid(site.location ~ latrine.present)

```
:::

# Exploratory Data Analysis

## Outliers - box/violin plots

::: panel-tabset
### All

```{r}
ggplot(df_latPlot, aes(name, value, fill = name)) + geom_boxplot() + facet_grid(site.location ~ latrine.present)
```

### Road

```{r}
ggplot(df_latT, aes(site.location, droad)) + 
  geom_violin() + 
  facet_grid(~latrine.present)
```

### Cabin

```{r}
ggplot(df_latT, aes(site.location, dcabin)) + 
  geom_violin() + 
  facet_grid(~latrine.present)
```

### Logging

```{r}
ggplot(df_latT, aes(site.location, dlogging)) + 
geom_violin() + 
  facet_grid(~latrine.present)
```

### Stream mouth

```{r}
ggplot(df_latT, aes(site.location, dstreammouth)) + 
  geom_violin() + 
  facet_grid(~latrine.present)
```

### Freshwater

```{r}
ggplot(df_latT, aes(site.location, dfreshwater)) + 
  geom_violin() + 
  facet_grid(~latrine.present)
```

### Forage Area

```{r}
ggplot(df_latT, aes(site.location, dforagearea)) + 
  geom_violin() + 
  facet_grid(~latrine.present)
```
:::

## Outliers-Cleavland

::: panel-tabset
### Road

```{r}
ggplot(df_latT, aes(droad, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```

### Cabin

```{r}
ggplot(df_latT, aes(dcabin, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```

### Logging

```{r}
ggplot(df_latT, aes(dlogging, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```

### Stream

```{r}
ggplot(df_latT, aes(dstreammouth, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```

### Freshwater

```{r}
ggplot(df_latT, aes(dfreshwater, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```

### Forage Area

```{r}
ggplot(df_latT, aes(dforagearea, y = seq(1, length(droad),1), fill = site.location, colour = site.location)) + geom_point() + ylab("ID") + facet_grid(~latrine.present)
```
:::

## Zeros/Collinearity

::: panel-tabset
### zeros

```{r}
table(df_latT$lat.pres, df_latT$site.location) 
```

### collinearity/relationship

```{r}
#| warnings: false
Scatter_Matrix <- ggpairs(df_latT,columns = c(2:7, 9), title = "Scatter Plot Matrix for latrine Dataset", axisLabels = "show") 
Scatter_Matrix
```
:::

## Interactions

Coplots area a little tricky to read. The gray bars represent the coverage of the variable in relation to the row or column, i.e., the bars on the right are for the rows (read bottom to top) and the bars on top are for the columns (read left to right).

::: panel-tabset
### Road-cabin

```{r}
coplot(droad ~ dcabin |lat.pres*site.location, data = df_latT)
```

### Road-logging

Is only relevant for Alexander Bay - no measurements for TN

```{r}
coplot(droad ~ dlogging |lat.pres*site.location, data = df_latT)
```

### Road-stream

```{r}
coplot(droad ~ dstreammouth |lat.pres*site.location, data = df_latT)
```

### Road-fresh

```{r}
coplot(droad ~ dfreshwater  |lat.pres*site.location, data = df_latT)
```

### Road-forage

```{r}
coplot(droad ~ dforagearea  |lat.pres*site.location, data = df_latT)
```

### Cabin-logging

```{r}
coplot(dcabin ~ dlogging |lat.pres*site.location, data = df_latT)
```

### Cabin-stream

```{r}
coplot(dcabin ~ dstreammouth |lat.pres*site.location, data = df_latT)
```

### Cabin-fresh

```{r}
coplot(dcabin ~ dfreshwater |lat.pres*site.location, data = df_latT)
```

### Cabin-forage

```{r}
coplot(dcabin ~ dforagearea |lat.pres*site.location, data = df_latT)
```

### Logging-stream

```{r}
coplot(dlogging ~ dstreammouth |lat.pres*site.location, data = df_latT)
```

### Logging-fresh

```{r}
coplot(dlogging ~ dfreshwater |lat.pres*site.location, data = df_latT)
```

### Logging-forage

```{r}
coplot(dlogging ~ dforagearea |lat.pres*site.location, data = df_latT)
```

### Stream-fresh

```{r}
coplot(dstreammouth ~ dfreshwater |lat.pres*site.location, data = df_latT)
```

### Stream-forage

```{r}
coplot(dstreammouth ~ dforagearea |lat.pres*site.location, data = df_latT)
```

### Fresh-forage

```{r}
coplot(dfreshwater ~ dforagearea |lat.pres*site.location, data = df_latT)
```
:::

# Analysis

```{r}
m1 <- glm(lat.pres ~ droad + site.location + dlogging, 
          family = binomial(link = "logit"),
          data = df_latT)
```

## Diagnostics

I spent sometime trying to figure out why there are so many warnings with the diagnostics - see otter_analysis.R

::: panel-tabset
### Homogeneity-normality

```{r}
library(DHARMa)
m1_simres <- simulateResiduals(m1)
plot(m1_simres) 
```

### Independence
:::

```{r}
print("Hi")
```

## Confirmatory Statistics

::: panel-tabset
### Summary

```{r}
summary(m1)
```

### Coefficients

```{r}
coef(m1)
```
:::

## Predictions

::: panel-tabset
### Road

```{r}
ggpredict(m1, terms = "droad") |> plot()
```

### Logging

```{r}
ggpredict(m1, terms = "dlogging") |> plot()
```

### Site

```{r}
ggpredict(m1, terms = "site.location") |> plot()
```

### Interaction

```{r}
ggpredict(m1, terms = c("site.location", "droad")) |> plot()
```
:::
